% Standalone wrapper to compile the resharing section.
% The full LP-073-pulsar paper is composed at ~/work/lux/papers/lp-073-pulsar/
% (parent directory under lux/papers/); this minimal wrapper exists so
% the section can be typechecked in isolation during development.
%
% Compile with: pdflatex lp-073-pulsar-resharing.tex (twice, for refs).

\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage{cleveref}

\hypersetup{colorlinks=true,linkcolor=black,citecolor=blue,urlcolor=blue}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{remark}{Remark}

\title{LP-073-pulsar: Proactive Secret Resharing for Pulsar Lattice Threshold Signatures}
\author{Lux Industries Inc}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
We adapt the Herzberg-Jakobsson-Jarecki-Krawczyk-Yung 1997 proactive
secret-sharing protocol to the lattice ring $R_q = \mathbb{Z}_q[X]/(X^{256}+1)$
used by Pulsar lattice threshold signatures, allowing the validator-set
rotation problem of Quasar consensus to be solved without re-running
trusted-dealer key generation at every epoch boundary. The master secret
$s$ is preserved across rotations; only the share distribution changes.
The genesis-time public key $\tilde b$ is unchanged, so signatures from
any future epoch verify under the same public anchor.
\end{abstract}

\input{sections/06-resharing}

\begin{thebibliography}{99}
\bibitem{hjky97}
Amir Herzberg, Markus Jakobsson, Stanis\l{}aw Jarecki, Hugo Krawczyk, Moti Yung.
``Proactive secret sharing or: How to cope with perpetual leakage.''
\emph{CRYPTO 1995/1997}.
\bibitem{desmedt-jajodia97}
Yvo Desmedt, Sushil Jajodia.
``Redistributing secret shares to new access structures and its applications.''
Technical Report ISSE TR-97-01, George Mason University, 1997.
\bibitem{shamir79}
Adi Shamir.
``How to share a secret.''
\emph{Communications of the ACM} 22(11):612--613, 1979.
\bibitem{wong02}
Theodore M.\ Wong, Chenxi Wang, Jeannette M.\ Wing.
``Verifiable secret redistribution for archive systems.''
In \emph{Proceedings of the First International IEEE Security in Storage Workshop}, 2002.
\bibitem{lp020}
LP-020. ``Quasar Consensus: Triple-Sign with BLS, Ringtail, and ML-DSA.''
\bibitem{lp070}
LP-070. ``ML-DSA-65 Identity Layer for Quasar Validators.''
\bibitem{lp073}
LP-073. ``Ringtail: A Two-Round MAC-Authenticated Lattice-Based Threshold Signature.''
\end{thebibliography}

\end{document}
