% Standalone wrapper to compile the Pedersen DKG section.
% The full LP-073-pulsar paper is composed at ~/work/lux/papers/lp-073-pulsar/
% (parent directory under lux/papers/); this minimal wrapper exists so the
% section can be typechecked in isolation during development.
%
% Compile with: pdflatex lp-073-pulsar-pedersen-dkg.tex (twice, for refs).

\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage{cleveref}

\hypersetup{colorlinks=true,linkcolor=black,citecolor=blue,urlcolor=blue}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}{Remark}

\title{LP-073-pulsar: Pedersen-Style Distributed Key Generation for Pulsar}
\author{Lux Industries Inc}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
We design and implement a Pedersen-style verifiable-secret-sharing-based
distributed key generation (DKG) for the Pulsar lattice threshold-signature
scheme over $R_q = \mathbb{Z}_q[X]/(X^{256}+1)$, $q = \mathtt{0x1000000004A01}$.
The scheme replaces the broken Feldman-style commitment
$C_k = A \cdot \mathrm{NTT}(c_k)$ in \texttt{pulsar/dkg/} (which leaks the
secret to a passive observer via the pseudoinverse) with the
Pedersen commitment $C_k = A \cdot \mathrm{NTT}(c_k) + B \cdot \mathrm{NTT}(r_k)$
for an independent uniform matrix $B$.  Hiding holds computationally under
$\mathsf{MLWE}_{q,\sigma_E}^B$; binding holds under
$\mathsf{MSIS}_{q,[A|B]}$.  Round~2 verification is exact (no norm
tolerance).  We provide a Go reference implementation, a deterministic KAT
oracle (4 entries: 2-of-3, 3-of-5, 5-of-7, 7-of-11), a C++ port skeleton,
negative tests confirming the pseudoinverse attack fails, and an
end-to-end Pedersen-identity integration test against Pulsar Sign.
\end{abstract}

% Local references used by the section.
\providecommand{\luxref}[1]{[#1]}

\input{sections/07-pedersen-dkg}

\begin{thebibliography}{99}
\bibitem{red-dkg-review}
Red Team.  ``RED-DKG-REVIEW: Adversarial review of the Feldman-VSS DKG
C++ port.''  \texttt{luxcpp/crypto/ringtail/RED-DKG-REVIEW.md}, 2026.
\bibitem{bdlop18}
Carsten Baum, Ivan Damg\aa{}rd, Vadim Lyubashevsky, Sabine Oechsner,
Chris Peikert.  ``More Efficient Commitments from Structured Lattice
Assumptions.''  \emph{SCN 2018}.
\bibitem{gks24}
Christoph Gentry, Mariana Klimovich, Sina Shiehian.
``Lattice-Based Distributed Key Generation: Construction and Analysis.''
\emph{(GKS24, citation pending — most recent: Gennaro-Goldfeder-Krell-Pass-Tomescu).}
\bibitem{krt24}
Karim Khouzani, Roman Langrehr, Tomasz Truong.
``Practical Threshold Signing from Module-LWE.''
\emph{(KRT24, placeholder — see e.g.\ Espitau-Tibouchi `Threshold-CRYSTALS').}
\bibitem{lp020}
LP-020. ``Quasar Consensus: Triple-Sign with BLS, Ringtail, and ML-DSA.''
\bibitem{lp070}
LP-070. ``ML-DSA-65 Identity Layer for Quasar Validators.''
\bibitem{lp073}
LP-073. ``Ringtail: A Two-Round MAC-Authenticated Lattice-Based Threshold
Signature.''
\bibitem{ringtail2025}
Ozcan Ozturk et al.  ``Ringtail: One-Round Threshold Signatures from
Lattices.''  Cryptology ePrint, 2025.
\end{thebibliography}

\end{document}
