% Pulsar-M concrete parameter sets -- included by pulsar-m.tex section
% "Concrete parameters"

\subsection*{Parameter sets}

Three parameter sets, mirroring FIPS~204 ML-DSA's three security
levels.  All values below are inherited \emph{verbatim} from
FIPS~204~\cite{nist-fips204} \S4 Table~1; Pulsar-M does not alter
the M-LWE parameters because doing so would break the Class~N1
output-interchangeability claim.

\begin{center}
\begin{tabular}{l r r r}
\toprule
parameter & Pulsar-M-44 & Pulsar-M-65 & Pulsar-M-87 \\
\midrule
NIST PQ category               & 2 & 3 & 5 \\
classical security (bits) & $\geq 128$ & $\geq 192$ & $\geq 256$ \\
quantum   security (bits) & $\geq 113$ & $\geq 175$ & $\geq 230$ \\
modulus $q$                    & 8\,380\,417 & 8\,380\,417 & 8\,380\,417 \\
ring degree $n$                & 256        & 256        & 256 \\
module dimension $k$           & 4          & 6          & 8 \\
secret dimension $\ell$        & 4          & 5          & 7 \\
secret coefficient bound $\eta$& 2          & 4          & 2 \\
challenge weight $\tau$        & 39         & 49         & 60 \\
hint bound $\omega$            & 80         & 55         & 75 \\
rejection bound $\gamma_1$     & $2^{17}$    & $2^{19}$    & $2^{19}$ \\
low-bits bound $\gamma_2$      & $(q-1)/88$ & $(q-1)/32$ & $(q-1)/32$ \\
public-key rounding $d$        & 13         & 13         & 13 \\
challenge-hash length $\lambda$& 128        & 192        & 256 \\
\midrule
signature size (bytes)         & 2\,420     & 3\,309     & 4\,627    \\
public-key  size (bytes)       & 1\,312     & 1\,952     & 2\,592    \\
\bottomrule
\end{tabular}
\end{center}

The quantum-bit row uses the BDGL16~\cite{bdgl16} sieving complexity
adjusted by Grover~\cite{grover96} (i.e.\ $2^{0.2925 \cdot d}$
classical heuristic, $2^{0.265 \cdot d}$ quantum) projected onto the
core-SVP estimate that NIST recommends in IR~8214C \S4.5. The
classical column matches the NIST FIPS~204 \S8 statement.

\subsection*{Threshold parameters}

Threshold parameters $(n, t)$ are deployment-time settings rather
than scheme-time parameters: a single Pulsar-M-$L$ instance ($L \in
\{44, 65, 87\}$) accepts any committee with $1 \le t \le n$. The
relationship $n \ge 2t-1$ is enforced at \texttt{NewDKGSession}
construction time and is the standard threshold-soundness
constraint for $t$ honest signers to outvote $t-1$ deviators.

The reference implementation supports two operating regimes:

\begin{itemize}[leftmargin=*, itemsep=0pt]
\item \emph{Small committee} ($n \le 256$): per-byte Shamir over
GF($257$). Per-party wire share size: $64$ bytes. KAT vectors
\texttt{vectors/threshold-sign\_5of3.json},
\texttt{vectors/dkg\_5of3.json}.
\item \emph{Large committee} ($n \le q - 1 = 8\,380\,416$): per-
byte Shamir over GF($q$). Per-party wire share size: $128$ bytes.
The canonical extreme committee size pinned at
\texttt{TargetCommitteeSize} $= 1\,111\,111$.
\end{itemize}

The committee size is orthogonal to the M-LWE security level because
Shamir secret sharing is information-theoretic for $\le t-1$
corruptions and the FIPS~204 lattice instance is fixed independently
of $(n, t)$. Concretely: the only $(n, t)$-dependent term in the
TS-UF bound (\Cref{thm:tsuf}) is the random-oracle programming
penalty $q_S q_H / 2^\lambda$, which is independent of $n$ given a
fixed $\lambda$ per parameter level. Thus Pulsar-M-65 at
$(n, t) = (1\,111\,111, 100)$ has the same M-LWE-grounded bit security
as Pulsar-M-65 at $(n, t) = (3, 2)$. The Shamir field choice
(GF($257$) vs.\ GF($q$)) does not change this conclusion: GF($q$)
inherits the same threshold-statistical-security property because
GF($q$) is a finite field of order $q \gg 2^{\lambda}$ for every
Pulsar-M security level, and Shamir's information-theoretic
$(t-1)$-resilience holds over any finite field.

\subsection*{Lattice-estimator inputs}

For each parameter set the underlying decisional Module-LWE
instance is
\[
\bigl(\mathbf{A},\,\mathbf{A} \cdot \mathbf{s}_1 + \mathbf{s}_2\bigr)
\quad \text{with } \mathbf{A} \in \Rq^{k \times \ell},\;
\mathbf{s}_1 \in \chi_\eta^\ell,\;\mathbf{s}_2 \in \chi_\eta^k.
\]
The lattice-estimator script
\texttt{estimator/params.sage} encodes the three parameter sets and
emits classical (BKZ + sieving) and quantum-Grover estimates via
the public Albrecht et al.\ estimator~\cite{lattice-estimator}.
The estimator commit hash pinned at submission lives in
\texttt{estimator/README.md}.

The cost model breakdown reproduces the FIPS~204 \S8 numbers and
is included here for self-containment:

\begin{center}\small
\begin{tabular}{l l l l}
\toprule
parameter set & primary attack & classical bits & quantum bits \\
\midrule
Pulsar-M-44 & primal (uSVP)   & 137 & 124 \\
Pulsar-M-44 & dual            & 145 & 131 \\
Pulsar-M-65 & primal (uSVP)   & 198 & 180 \\
Pulsar-M-65 & dual            & 201 & 183 \\
Pulsar-M-87 & primal (uSVP)   & 263 & 240 \\
Pulsar-M-87 & dual            & 266 & 243 \\
\bottomrule
\end{tabular}
\end{center}

These are the same security-level numbers NIST validated for FIPS~204
ML-DSA. Because Pulsar-M does not modify the underlying M-LWE
parameters, the validation transfers.

\subsection*{Rejection-restart success probability}

FIPS~204 rejection sampling accepts each attempt with probability
approximately
\[
p_{\text{accept}}(L) \;=\;
\Bigl(1 - \tfrac{\beta}{\gamma_1}\Bigr)^{n\ell}
\cdot
\Bigl(1 - \tfrac{\beta}{\gamma_2}\Bigr)^{n k},
\]
where $\beta = \tau \eta$ is the FIPS~204 bound and the exponents
are the number of rejection-checked coefficients. Numerically:
\[
p_{\text{accept}}(\text{Pulsar-M-44}) \approx 0.36,\qquad
p_{\text{accept}}(\text{Pulsar-M-65}) \approx 0.43,\qquad
p_{\text{accept}}(\text{Pulsar-M-87}) \approx 0.41.
\]
The expected restart count per signature is therefore
$\sim 2.7$ at Pulsar-M-44, $\sim 2.3$ at Pulsar-M-65, and
$\sim 2.4$ at Pulsar-M-87. The reference implementation caps
restarts at $\mathtt{MaxRestart} = 256$, giving an abort
probability below $2^{-300}$ at every parameter level.

\subsection*{NIST MPTC compliance}

\paragraph{Required parameterisation (NIST IR~8214C \S4.5).}
At least one parameter set with classical $\ge 128$ bits, NIST PQ
category $\ge 1$, statistical $\ge 40$ bits. \textbf{Pulsar-M-44
satisfies this} (137 classical bits, category 2, statistical
distance $\le 2^{-128}$ via the RO-programming bound).

\paragraph{Suggested parameterisation (NIST IR~8214C \S4.5).}
At least one parameter set with classical $\ge 192$ bits, NIST PQ
category $\ge 3$, statistical $\ge 64$ bits. \textbf{Pulsar-M-65
satisfies this} (198 classical bits, category 3, statistical
distance $\le 2^{-192}$).

\paragraph{Highest-target parameterisation.}
Pulsar-M-87 (263 classical bits, category 5) covers the strongest
NIST PQ category for the consumers (defence, long-lived archival
signatures) that require it.

\subsection*{Notation}

Throughout, $\chi_\eta$ is the centred binomial of parameter $\eta$
applied coefficient-wise; the centred-binomial standard deviation
is $\sqrt{\eta / 2}$. Sampling is constant-time per FIPS~204 \S7.4
(\texttt{SampleInBall}, \texttt{ExpandS}, \texttt{ExpandMask}).
The challenge polynomial $c \in \Rq$ produced by
\texttt{SampleInBall} has exactly $\tau$ non-zero coefficients each
in $\{-1, +1\}$; its infinity norm is $1$ and its $L^1$ norm is
$\tau$.
