% Pulsar-M Notes on Patent Claims -- included by pulsar-m.tex.
% Mirrors docs/patent-notes-draft.md (now deleted; this file is the
% submission-package patent-claims appendix).

\paragraph{Required by NIST MPTC IR 8214C \S5} as a package
deliverable. This document is collected over the development period
and finalized for the submission.

\subsection{Status}

\textbf{Draft.} No patent claims have been formally identified. This
appendix tracks claims as contributors disclose them.

\subsection{Inherited from upstream}

\paragraph{Pulsar (\texttt{luxfi/pulsar}).}
Pulsar-M reuses Pulsar's protocol structure. Pulsar's IP posture per
its README:

\begin{itemize}[leftmargin=*, itemsep=0pt]
\item Apache-2.0 licensed.
\item Patent grant per Apache 2.0 \S3 from each contributor.
\item No known active patent claims as of repository creation.
\end{itemize}

This applies to Pulsar-M to the extent that Pulsar-M code or
protocol elements are derivative of Pulsar.

\paragraph{Ringtail (\texttt{luxfi/ringtail}).}
Pulsar (and therefore Pulsar-M) is a fork of academic Ringtail.
Ringtail (ePrint 2024/1113) authors: Cecilia Boschini, Darya
Kaviani, Russell W. F. Lai, Giulio Malavolta, Akira Takahashi, Mehdi
Tibouchi. Ringtail's open-source repo is Apache-2.0 with no asserted
patent claims as of mid-2026. Pulsar-M's M-LWE adaptation does not
import Ringtail code directly but inherits the protocol structure.

\paragraph{ML-DSA / FIPS 204.}
ML-DSA is a NIST-standardized algorithm. The Dilithium team's IP
disclosures during NIST PQC standardization are public on the NIST
PQC website. Pulsar-M targets output interchangeability with
FIPS~204 but does not assert any rights over FIPS~204 itself.

\subsection{Contributor disclosures}

Per \texttt{CONTRIBUTING.md}, every commit's \texttt{Signed-off-by}
line is taken as either:

\begin{enumerate}[leftmargin=*, itemsep=0pt]
\item An explicit assertion that the contributor has no relevant
patent claims, OR
\item A reference to a disclosed claim listed below.
\end{enumerate}

\begin{center}
\begin{tabular}{llll}
\toprule
date & contributor & type & disclosure \\
\midrule
2026-05-10 & Lux Industries Inc & initial repo & no claims asserted \\
\bottomrule
\end{tabular}
\end{center}

(Updated as contributions land.)

\subsection{Third-party patents we may need to navigate}

Live concerns to investigate before submission:

\begin{itemize}[leftmargin=*, itemsep=0pt]
\item Lattice-estimator usage (we use the open-source estimator;
license pass-through to MIT).
\item Gaussian sampler implementation (FIPS~204 references CDT;
alternate rejection samplers may have IP).
\item Polynomial multiplication via NTT (standard, no known IP).
\item Pedersen commitments (1991 paper, expired patents).
\end{itemize}

The submission's Notes on Patent Claims will explicitly call out
each of these.

\subsection{NIST MPTC submission requirements}

NIST IR 8214C \S5 (Notes on Patent Claims) requires:

\begin{quote}
Submitter(s) shall include a statement of any patent claims known
to them that may be relevant to the submitted package, regardless
of who owns the claim. Statements of ``no known claims'' are
acceptable.
\end{quote}

Our final statement, once the spec freezes:

\begin{quote}
\emph{To be drafted at spec freeze. Will incorporate every
disclosure in the contributor table above, every inherited claim
from Pulsar / Ringtail / ML-DSA, and the third-party investigation
outcome.}
\end{quote}

\subsection{Process}

\begin{enumerate}[leftmargin=*, itemsep=0pt]
\item Every PR review checks for new IP-relevant code.
\item Significant cryptographic additions (new sampling routine, new
commitment shape, new aggregation step) trigger an explicit IP
review with one of the sponsor's IP counsel.
\item Final statement assembled at freeze, included in
\texttt{spec/pulsar-m.pdf} Appendix~A.
\end{enumerate}
