% Pulsar system model -- included by pulsar.tex section "System model"

% ---------------------------------------------------------------
% Top of document inserts this file under the chapter heading
% "System model"; no \section* command here is appropriate
% because pulsar.tex provides one via the surrounding
% \section{System model}.

\paragraph{Network model.}
The protocols assume a partially synchronous network with three
channel primitives:

\begin{itemize}[leftmargin=*, itemsep=0pt]
\item \textbf{Authenticated broadcast.} Every party broadcasts via a
total-order channel (Lux consensus) that is FIFO per sender and
eventually delivered to every honest party within a known bound
$\Delta$ after global stabilisation. Within a round window the
honest parties are assumed to receive every honest broadcast; outside
the window the protocol re-runs (\Cref{game:rob}).
\item \textbf{Point-to-point.} Each ordered pair of parties shares an
authenticated, encrypted channel using long-term identity keys
(production: Ed25519 + Noise XK; reference: TLS 1.3 mutual auth).
DKG Round-1 envelopes and the per-pair MAC keys flow over this
channel.
\item \textbf{Public bulletin.} The Lux consensus log itself is the
append-only authenticated bulletin: $\mathit{pk}$, commitments,
signed complaints, signatures, and beacon values are all anchored
in finalised blocks. Bulletin entries are immutable, totally
ordered, and observable by every participant.
\end{itemize}

Full asynchrony is out of scope for round-1 MPTC and is recorded as
a round-2 open question in \S\ref{sec:knownlimits}.

\paragraph{Setup assumptions.}
\begin{itemize}[leftmargin=*, itemsep=0pt]
\item \textbf{PKI.} Each party advertises a long-term identity
verification key in the Lux consensus validator-set record per
HIP-0077. This key signs complaints (\Cref{sec:abort}) and the
DKG / Reshare activation certificates.
\item \textbf{Random beacon.} The chain randomness layer (Lux Quasar)
provides an unbiasable beacon $\beta_e$ at every epoch boundary $e$.
$\beta_e$ is committed in the post-finalisation header of epoch $e$
and is unpredictable in advance of corruption decisions for that
epoch (the beacon-unbiasability assumption invoked by
\Cref{thm:reshare-priv} and \Cref{thm:mob}).
\item \textbf{Common reference string.} The public matrices
$\mathbf{A}, \mathbf{B} \in \Rq^{k \times \ell}$ derive from
nothing-up-my-sleeve seeds: $\rho$ is the chain genesis randomness,
$\rho_B$ is its $\cSHAKE$ image with the customisation tag
\texttt{PULSAR-M-EXPANDB-V1} (\S\ref{sec:prelim-pedersen}).
\end{itemize}

\paragraph{Trust model.}
\begin{itemize}[leftmargin=*, itemsep=0pt]
\item \textbf{Static corruption.} Up to $t-1$ parties out of $n$ are
controlled by a $\PPT$ adversary $\mathcal{A}$ from the start of the
ceremony. $\mathcal{A}$ observes the protocol transcript and may
deviate arbitrarily from the prescribed protocol on the corrupted
parties' behalf. This is the round-1 MPTC adversarial model and is
captured by \Cref{game:tsuf}.
\item \textbf{Mobile corruption.} Across epochs the adversary may
re-select its corruption set: at each epoch $e$ a fresh
$\mathcal{C}_e$ with $|\mathcal{C}_e| \le t-1$ is chosen, leaked,
and (between epochs) un-corrupted in the sense that the party
forgets its epoch-$e$ secrets. This is captured by \Cref{game:mob}
and reduces to TS-UF plus beacon-unbiasability plus M-LWE.
\item \textbf{Adaptive corruption.} The strongest in-game adaptive
model is recorded as \Cref{game:adapt}; the formal proof is
deferred to round 2 (see \S\ref{sec:knownlimits}).
\end{itemize}

The honest-participation requirement for liveness is $n - t + 1$
honest parties at every round. Honest-participation below this
threshold makes a complete protocol round impossible and triggers a
liveness-only abort (no security loss, but no signature output until
the network heals).

\paragraph{Abort model.}
\begin{itemize}[leftmargin=*, itemsep=0pt]
\item \textbf{Identifiable abort.} Every detected deviation produces
a signed \textsc{Complaint} record identifying the deviating party
\emph{by long-term identity key}. The complaint structure is
specified in \S\ref{sec:abort} and is publicly verifiable from the
transcript alone.
\item \textbf{Slashing.} The Lux consensus governance layer consumes
complaints; a quorum of distinct accusers against the same accused
within one epoch is a disqualification event with on-chain
slashing consequences. The slashing rule is out of scope for this
document; we specify only the complaint format and the threshold
soundness arguments (\Cref{thm:rob}).
\end{itemize}

\paragraph{Preprocessing.}
\begin{itemize}[leftmargin=*, itemsep=0pt]
\item $\DKG$ runs once per validator-set epoch. Output: a fresh
$\mathit{pk}$ and per-party shares $(\mathbf{s}_i, \mathbf{u}_i)$.
\item $\Reshare$ runs at every validator-set change (typically every
few hours to days). Output: new shares against the unchanged
$\mathit{pk}$.
\item $\Refresh$ (zero-polynomial $\Reshare$) runs as a background
hygiene step at hourly cadence within a stable validator set.
\item $\Sign$ runs per signature request and is preprocessing-free
at the protocol layer (per-round randomness is recomputed each
attempt). An optional Round-0 mask precomputation is available
for low-latency targets and is described in
\S\ref{sec:impl-rejection-restart}.
\end{itemize}

\paragraph{Rotation.}
The reshare protocol of \S\ref{sec:reshare} rotates the share
distribution without changing $\mathit{pk}$
(\Cref{thm:reshare-pkinv}). Members may join, leave, or be
disqualified between epochs subject to the $(n', t')$ constraint
$n' \ge 2t' - 1$ on the new committee. Rotation cadence is governed
by the validator-set epoch (typically 12 hours to 7 days on Lux).

\paragraph{Committee scale.}
Pulsar's per-byte Shamir layer supports two operating regimes:

\begin{itemize}[leftmargin=*, itemsep=0pt]
\item \emph{Small committee} ($n \le 256$). Shares are dealt over
GF(257) with 64-byte wire encoding. This is the regime used by the
Lux primary network's validator set today and matches the
GF(257)-fast-path KAT vectors in \texttt{vectors/}.
\item \emph{Large committee} ($n \le q - 1 = 8\,380\,416$). Shares
are dealt over GF($q$) with 128-byte wire encoding, where $q$ is
the FIPS~204 prime $2^{23} - 2^{13} + 1$. The reference
implementation pins the canonical extreme committee size at
$N^* = \mathtt{TargetCommitteeSize} = 1\,111\,111$ -- well above
the round-1 MPTC suggested ceiling and the practical bar of
$N > 10^4$ -- so that the protocol's algebraic correctness has
been exercised at over four orders of magnitude beyond any
deployment currently planned in production. The wide-field path
is mandatory whenever $n > 256$.
\end{itemize}

Both regimes produce identical FIPS~204 signature bytes; the field
choice never propagates past the per-quorum DKG / Sign boundary and
is therefore not visible to FIPS~204 verifiers. See
\S\ref{sec:parameters} for the corresponding party-count entries
and \S\ref{sec:impl} for the auto-selection rule embedded in the
reference implementation.

\paragraph{Committee selection and PQ rollup (production).}
The canonical Lux deployment does \emph{not} run one $1\,111\,111$-
party DKG ceremony. Instead it composes three orthogonal layers:

\begin{enumerate}[leftmargin=*, itemsep=0pt]
\item \emph{Grouped sortition.} The Lux consensus layer
(\texttt{consensus/protocol/quasar/grouped\_threshold.go}) splits
the $N \approx 1.1$M-validator pool into $\sim N / 3$ groups of size
$3$ using deterministic SHA3-384 Fisher-Yates shuffle. The
sortition seed is an epoch-bound chain digest, making it
unpredictable in advance of group composition.
\item \emph{Per-group Pulsar (3, 2).} Each group runs the small-
committee Pulsar path at $(T, N) = (2, 3)$ -- the canonical
small-committee config. The group produces one FIPS~204 ML-DSA
signature per epoch checkpoint. Tolerates one Byzantine party per
group. Per-group DKG / Sign / Reshare cost is constant in the
total validator-pool size.
\item \emph{P3Q STARK rollup.} All per-group ML-DSA signatures roll
up via P3Q (Lux's strict-PQ Plonky3 fork: STARK + FRI over
Goldilocks, cSHAKE256 Merkle, FIPS 202 + SP 800-185 hash family).
The chain pins
\texttt{ProofBackendP3QSTARKFRISHA3 = 0x22} in
\texttt{consensus/config/pq\_mode.go}; the proof-backend registry
explicitly forbids
\texttt{ProofBackendGroth16WrapForbid = 0x80} and
\texttt{ProofBackendKZGWrapForbid = 0x81} so no pairing-based
classical proof system can leak in. The final certificate carries
a single P3Q proof; verification time is constant in the total
signer count.
\end{enumerate}

The composition is \emph{fully post-quantum end-to-end}: every
primitive in the stack rests on post-quantum hardness assumptions.

\begin{center}\small
\begin{tabular}{l l l}
\toprule
layer & primitive & PQ hardness \\
\midrule
per-validator identity sig  & ML-DSA-65 (FIPS~204)               & Module-LWE + MSIS \\
per-group threshold sign    & Pulsar (2, 3) $\to$ FIPS~204 sig & Module-LWE + MSIS \\
sortition                   & SHA3-384 Fisher-Yates              & SHA-3 collision-resistance \\
inter-group rollup          & P3Q STARK + FRI                    & cSHAKE256 collision-resistance \\
final cert verifier         & P3Q verifier                       & cSHAKE256 collision-resistance \\
\bottomrule
\end{tabular}
\end{center}

There is no pairing, no elliptic-curve recursion, no KZG, no Groth16
anywhere in the production path. Shor's algorithm has no purchase on
any layer.

\paragraph{Why Pulsar does not need to scale to 1.1M parties.}
A naive scaling approach would run one Pulsar ceremony over all
$1.1$M validators. This costs $O(n^2)$ communication
($\sim 10^{12}$ envelopes), which is physically infeasible. The
grouped-sortition + P3Q-rollup architecture sidesteps the quadratic
ceiling: each Pulsar ceremony runs at constant size $(T, N) =
(2, 3)$, and the inter-group attestation runs as one P3Q proof.
The wide-field GF($q$) Pulsar path documented in this section is
the alternative single-large-committee deployment for permissioned
consortium / audit-attestation scenarios where the grouped
sortition layer is not appropriate.

\paragraph{Integer-arithmetic discipline.}
Every modular operation in Pulsar's core path uses uint32 lanes
with uint64 accumulators. The widest intermediate is one Lagrange
multiplication over GF($q$), which spans at most 46 bits. uint128
and uint256 widths are explicitly \emph{not} required by this
protocol; they are reserved for the Z-Chain SNARK side (which
operates over $\sim$254-bit prime-order fields). This discipline
gives constant-cycle modular arithmetic on every supported CPU
(x86\_64, aarch64, RISC-V64), as well as on GPU dispatch backends
(Apple Metal, NVIDIA CUDA, AMD ROCm) that natively support the
uint32 / uint64 pair.

\paragraph{Monitoring and observability.}
\begin{itemize}[leftmargin=*, itemsep=0pt]
\item \textbf{Public artefacts.} $\mathit{pk}$, all commitments, all
broadcast messages, signed complaints, final signatures, beacon
values $\beta_e$, and per-party identity-key signatures. These are
safe to log at any verbosity level.
\item \textbf{Private artefacts.} Shares
$\{\mathbf{s}_i, \mathbf{u}_i\}$, blinding factors $\mathbf{r}_{i,k}, g_i(j)$,
per-round masks $\mathbf{y}_i$, sampled secret values, PRNG seeds,
and norm-check intermediate values. These MUST NOT be logged at
any verbosity level (DD-007). The reference implementation enforces
this with a CI lint that rejects \texttt{log.*} and
\texttt{fmt.Print*} calls in \texttt{ref/go/pkg/pulsarm/}.
\end{itemize}

\paragraph{Deployment surface.}
The reference implementation is pure software (Go). Production
deployments are expected to integrate the share custody with an
HSM-backed key store (or equivalent secret-enclave technology); the
HSM exposes only Round-2 contributions and never reveals the share
in cleartext. HSM integration is out of scope for round-1 MPTC and
is recorded as a round-2 hardening item in \S\ref{sec:knownlimits}.

\paragraph{Failure recovery.}
On any disqualification event the chain layer removes the
disqualified party from the validator set and triggers an immediate
$\Reshare$ to a new committee. Liveness is preserved provided fewer
than $t-1$ parties are disqualified per epoch; beyond that bound the
chain enters a recovery mode that re-runs $\DKG$ from scratch with a
new committee derived from the stake-weighted validator set.

\paragraph{Cross-implementation conformance.}
The Go reference (\texttt{ref/go/}) and the eventual C reference
(\texttt{ref/c/}) MUST produce byte-equal outputs from the same
seeded inputs. KAT replay (\S\ref{sec:vectors}) is the conformance
gate. The KAT generation oracle is locked at
\texttt{cmd/pulsar-oracle}; both references replay it without
modification.
