\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[margin=1in]{geometry}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\theoremstyle{remark}\newtheorem{remark}{Remark}
\title{Pulsar Threshold ML-DSA via Boundary-Cleared Nonces and Carry
Elimination\\(No MPC, No TEE) --- BCC0 / BCC+}
\author{Lux Core Team --- \texttt{github.com/luxfi/pulsar}}
\date{}
\begin{document}
\maketitle

\section{The leak this replaces}
The v0.3/v0.4 \texttt{AlgebraicAggregate} path reconstructs $c\,\mathbf
s_2^{\mathrm{joint}}$ and $c\,\mathbf t_0^{\mathrm{joint}}$ at the
aggregator to form the FIPS hint. But $\mathbf s_2^{\mathrm{joint}}$ is
the master $\mathbf s_2$ (Shamir reconstruction) and $c$ is public and
varies per session, so revealing $c\,\mathbf s_2^{\mathrm{joint}}$ over
sessions is a linear system in the fixed $\mathbf s_2$ --- one invertible
$c$ recovers it; then $A\mathbf s_1 = \mathbf t - \mathbf s_2$ recovers
$\mathbf s_1$, a total key break. In the leaderless model every quorum
member aggregates, so every corrupt validator learns it. \textbf{Masking
the per-party shares does not help: the masks cancel in the aggregate the
protocol must reconstruct.} The cure is never to form the secret residual.

\section{The invariant and the whole game}
With $\mathbf w = A\mathbf y$, $\mathbf z = \mathbf y + c\,\mathbf s_1$,
$\mathbf t = A\mathbf s_1 + \mathbf s_2 = \mathbf t_1 2^d + \mathbf t_0$,
the verifier recomputes
\[
  \mathbf w' \;=\; A\mathbf z - c\,\mathbf t_1 2^d
  \;=\; \mathbf w + c\,\mathbf t_0 - c\,\mathbf s_2
  \;=\; \mathbf w + \Delta, \qquad \Delta := c\,\mathbf t_0 - c\,\mathbf
  s_2,
\]
and accepts iff $\mathrm{UseHint}(\mathbf h, \mathbf w') = \mathbf w_1$
where $\mathbf w_1 = \mathrm{HighBits}(\mathbf w)$ fixed $c = H(\mu \| \mathbf
w_1)$.
\begin{theorem}[No-leak target]
Produce a public $\mathbf h$ with $\mathrm{UseHint}(\mathbf h, \mathbf w +
\Delta) = \mathrm{HighBits}(\mathbf w)$ \emph{without} revealing $\Delta$,
$\mathrm{LowBits}(\mathbf w + \Delta)$, $c\,\mathbf s_2$, $c\,\mathbf
t_0$, or $r_0$.
\end{theorem}

\section{Conformance rule (central invariant)}
\label{sec:rule}
\textbf{The final hint $\mathbf h$ must be determined by public
nonce-region certificates and the public challenge --- never by
reconstructing the secret residual.} For BCC0 the certificate guarantees
$\mathbf h = 0$; for BCC+ it guarantees a publicly-determined hint
pattern. \emph{Any implementation that computes $\mathbf h$ by first
forming $c\,\mathbf s_2$, $c\,\mathbf t_0$, $r_0$, or
$\mathrm{LowBits}(\mathbf w + \Delta)$ is non-conformant.} Note $\mathbf
w' = A\mathbf z - c\,\mathbf t_1 2^d$ is itself \emph{public} (computable
by the verifier from $A,\mathbf z,c,\mathbf t_1$); reading $\mathbf h$ off
$(\mathbf w', \mathbf w_1)$ reveals only $\mathbf h$, which is in the
signature anyway --- it is \emph{not} residual reconstruction.

\subsection{Full $\mathbf w$ must be hidden (PULSAR-V13-W-LEAK)}
The full commitment $\mathbf w = A\mathbf y$ must \emph{never} be public or
reconstructible by a $t-1$ coalition. Since $\mathbf w' = A\mathbf z -
c\,\mathbf t_1 2^d$ becomes public once $\mathbf z$ is assembled, anyone
holding full $\mathbf w$ computes $\mathbf w' - \mathbf w = c\,\mathbf t_0
- c\,\mathbf s_2 = \Delta$ --- the same long-term-secret residual as the
original leak. \textbf{Public:} $\mathbf w_1$, a commitment to $\mathbf w$,
a \emph{zero-knowledge} boundary-clearance proof, and the final $(\mathbf
z,\mathbf h,\text{sig})$. \textbf{Forbidden:} full $\mathbf w$, $\mathbf
w_i$ shares reconstructing it, $\mathrm{LowBits}(\mathbf w)$, $\mathbf w' -
\mathbf w$. Hence $\textsc{BoundaryClear}(\mathbf w)$ on \emph{public}
$\mathbf w$ is \textbf{debug-oracle only}; production replaces it with a ZK
proof that a hidden $\mathbf w = A\mathbf y$ satisfies the predicate,
revealing none of $\mathbf w$, $\mathrm{LowBits}(\mathbf w)$, or per-
coefficient distances. \textbf{Until that ZK machinery exists the BCC/CEF
signing path is prototype, not production.}

\section{Profiles}
\subsection{BCC0 --- conservative $\mathbf h = 0$}
Use only nonces whose hidden shift cannot move any coefficient across a
high-bit boundary: $\mathrm{HighBits}(\mathbf w + \Delta) =
\mathrm{HighBits}(\mathbf w)$, so $\mathbf h = 0$.
\begin{lemma}[BCC0 stability]\label{lem:bcc0}
$\textsc{BoundaryClear}(\mathbf w, B_\Delta) \wedge \|\Delta\|_\infty \le
B_\Delta \;\Rightarrow\; \mathrm{HighBits}(\mathbf w + \Delta) =
\mathrm{HighBits}(\mathbf w)$, whence $\mathrm{UseHint}(0, \mathbf w') =
\mathbf w_1$ and unmodified FIPS 204 accepts.
\end{lemma}
\textbf{BCC0 is infeasible for ML-DSA-65} (\S\ref{sec:bounds}): the worst-
case $B_\Delta$ exceeds $\gamma_2$, so no coefficient can clear. Retained
as a definition / fallback profile only, not used.

\subsection{BCC+ --- carry elimination, nonzero $\mathbf h$}
Allow $\mathbf h \neq 0$, but derive it from public data. The shift splits
into a \emph{small} part $-c\,\mathbf s_2$ and a \emph{large} part
$c\,\mathbf t_0$. Boundary-clear \emph{only} the small part; the large
part is resolved by the public hint.
\begin{definition}[Per-coefficient region]
For coefficient $w_j$ and margin $B$ (covering $\|c\,\mathbf
s_2\|_\infty$), classify by FIPS \texttt{Decompose}:
$\textsc{SafeZeroCarry}$ if $\mathrm{dist}(w_j) > B$ and the $c\,\mathbf
t_0$ carry cannot cross; $\textsc{SafeKnownCarry}$ if the carry is
resolvable to a single public bit from $\mathbf w'$; $\textsc{Unsafe}$
otherwise. Accept a nonce iff no coefficient is $\textsc{Unsafe}$.
\end{definition}
\begin{lemma}[BCC+ correctness]\label{lem:bccplus}
If $\textsc{BoundaryClear}(\mathbf w, 2\beta)$ (clears $c\,\mathbf s_2$)
and $\|c\,\mathbf t_0\|_\infty < \alpha$ (so each coefficient's high bits
move by at most $\pm 1$), then (i) $\mathrm{HighBits}(\mathbf w -
c\,\mathbf s_2) = \mathbf w_1$ and $\|\mathrm{LowBits}(\mathbf w -
c\,\mathbf s_2)\|_\infty < \gamma_2 - \beta$ (the FIPS $r_1{=}\mathbf
w_1$, $r_0$-norm conditions); and (ii) the public hint $h_j := [\,
\mathrm{HighBits}(w'_j) \neq w_{1,j}\,]$ equals the FIPS hint
$\mathrm{MakeHint}(-c\,\mathbf t_0, \mathbf w - c\,\mathbf s_2)$ and
satisfies $\mathrm{UseHint}(\mathbf h, \mathbf w') = \mathbf w_1$.
\end{lemma}
\emph{Reconciliation with ``region-derived'':} the $c\,\mathbf t_0$ carry
depends on the secret $\mathbf t_0$ and the online $c$, so it cannot be
fixed fully offline; the \emph{offline} certificate clears $c\,\mathbf
s_2$ and bounds the carry to $\pm 1$, and the \emph{online} step reads the
carry bit off the public $\mathbf w'$. Both inputs ($\mathbf w'$, $\mathbf
w_1$) are public; no residual is formed. This is BCC+ \S2A realised.

\section{Concrete bounds (ML-DSA-65)}
\label{sec:bounds}
$q{=}8380417,\ d{=}13,\ \tau{=}49,\ \eta{=}4,\ \gamma_2{=}261888,\
\alpha{=}2\gamma_2{=}523776,\ \beta{=}\tau\eta{=}196,\ \omega{=}55$.
\begin{itemize}
\item $\|c\,\mathbf s_2\|_\infty \le B_{s_2} = \tau\eta = 196$.
\item $\|c\,\mathbf t_0\|_\infty \le \tau\,2^{d-1} = 49\cdot4096 = 200704
  < \gamma_2 < \alpha$: the FIPS $\|c\,\mathbf t_0\|<\gamma_2$ check is
  \emph{vacuous} (always holds), and the carry moves $\mathrm{HighBits}$
  by at most $\pm1$ per coefficient. No check, no reconstruction.
\item \textbf{BCC0 infeasible:} needs clearance $> B_\Delta = B_{s_2} +
  \tau\,2^{d-1} \approx 401555 > \gamma_2 = 261888$ (max possible
  clearance). Yield $0$.
\item \textbf{BCC+ feasible:} clear only $c\,\mathbf s_2$ with margin $B =
  2\beta = 392$ (covers the $\mathrm{HighBits}$ boundary and the $r_0 <
  \gamma_2-\beta$ edge). Per-coefficient clear prob $\approx 1 -
  B/\gamma_2 = 0.9985$; all-$256{\cdot}6$ yield $\approx 0.10$ (measure;
  raise margin only, never lower). $c\,\mathbf t_0$ contributes the
  nonzero, $\omega$-sparse public hint.
\end{itemize}

\section{Proof obligations}
\paragraph{BCC0 chain (Lemma~\ref{lem:bcc0}).} $\mathbf w{=}A\mathbf y$;
$\mathbf z{=}\mathbf y{+}c\mathbf s_1$; $A\mathbf z{-}c\mathbf t_1 2^d
{=}\mathbf w{+}\Delta$; $\|\Delta\|_\infty\le B_\Delta$;
$\textsc{BoundaryClear}(\mathbf w,B_\Delta)$ $\Rightarrow$
$\mathrm{HighBits}(\mathbf w{+}\Delta){=}\mathbf w_1$ $\Rightarrow$
$\mathrm{UseHint}(0,\cdot){=}\mathbf w_1$ $\Rightarrow$ accept.
\paragraph{BCC+ / CEF chain (Lemma~\ref{lem:bccplus}).} as above with the
public hint; $h$ region/public-$\mathbf w'$-derived; for all $\Delta$ with
$\|\Delta\|_\infty\le B_\Delta$, $\mathrm{UseHint}(\mathbf h,\mathbf w{+}
\Delta){=}\mathbf w_1$.
\paragraph{Soundness.} A malicious signer's bad $\mathbf z_i$ yields a
wrong $\mathbf w'$ and a wrong $\mathbf h$ $\Rightarrow$ the mandatory
final unmodified-FIPS verify \emph{fails} (identifiable abort via the
per-party $\mathbf z_i$ proof/MAC). \textbf{Never fall back to forming
$c\,\mathbf s_2$/$c\,\mathbf t_0$/$r_0$.}
\paragraph{Transcript privacy / simulatability.} The transcript holds
$\{\mathbf w,\mathbf w_1,c,\mathbf z,\mathbf h,\text{commitments},
\text{proofs}\}$ and \emph{not} $c\,\mathbf s_{2,i}$, $c\,\mathbf
t_{0,i}$, $c\,\mathbf s_2^{\mathrm{joint}}$, $c\,\mathbf
t_0^{\mathrm{joint}}$, $\Delta$, $r_0$, $\mathrm{LowBits}(\mathbf
w{+}\Delta)$. A simulator reproduces it from $(pk, m, \text{final sig},
\text{signer bitmap}, \text{corrupt shares})$ without honest shares.
\paragraph{Conditioned-nonce security (hardest).} Conditioning the pool on
the public predicate $\textsc{BoundaryClear}(\mathbf w, 2\beta)$ (resp.\
$\textsc{AllRegionsSafe}$) must not weaken EUF-CMA: $\mathbf w = A\mathbf
y$ is independent of the key, and the surviving $\mathbf y$ distribution
must remain a valid rejection-sampled nonce distribution (or the signature
distribution must remain simulatable). \emph{This is a required proof, not
an assumption; if \textsc{2B nonce shaping} is used, the distribution
proof is mandatory before deployment.}

\section{Wire format (deletion audit)}
\textbf{Remove} \texttt{CS2}, \texttt{CT0} (and any \texttt{cs2},
\texttt{ct0}, \texttt{D2}, \texttt{D0}, \texttt{R0Share},
\texttt{LowBitsShare}, \texttt{HintInput}, \texttt{HintShare}) from the
Round-2 message and the $\tau_2$ transcript. Old fields fail
deserialization outside an explicit legacy-test parser.
\begin{verbatim}
type BoundaryNonceCert struct {
    NonceID [32]byte; PKEpoch uint64; CommitteeID [32]byte
    SignerSetRoot [32]byte; W1 PackedHighBits; WCommitment []byte
    ClearanceProof []byte; Margin uint32; CommitRoot [32]byte; Consumed bool }
    // NO full W field (PULSAR-V13-W-LEAK); W is debug-oracle only.
type ZPartial struct {
    PartyID PartyID; NonceID [32]byte; SessionID [32]byte
    ZShare PackedPolyVecL; Proof []byte; MAC []byte }
type PulsarSignature struct { C PackedChallenge; Z PackedPolyVecL; H PackedHint }
\end{verbatim}
No \texttt{CS2/CT0/D2/D0/R0Share/LowBitsShare/HintInput/HintShare}.

\section{Protocol}
\paragraph{Offline (message-independent) nonce pool.} Sample $\mathbf
y_i$; commit. The aggregate $\mathbf w = \sum\lambda_i\mathbf w_i$ is
\emph{hidden}: in production each signer proves in zero knowledge that the
hidden $\mathbf w$ is boundary-clear, publishing only $\mathbf w_1$, a
commitment to $\mathbf w$, and the clearance proof (PULSAR-V13-W-LEAK; the
debug oracle may form $\mathbf w$ to classify regions vs $B$). If
\textsc{AllRegionsSafe}, store the cert ($\mathbf w_1,\text{WCommitment},
\text{ClearanceProof},\text{CommitRoot}$); else discard. Run continuously off
the consensus path.
\paragraph{Online sign.} Pick an unused cert; $\mu = H(pk\|ctx\|m)$, $c =
H(\mu\|\mathbf w_1)$; collect $\mathbf z_i = \lambda_i\mathbf y_i +
c\lambda_i\mathbf s_{1,i}$; $\mathbf z = \sum\mathbf z_i$; reject to a
fresh nonce if $\|\mathbf z\|_\infty \ge \gamma_1-\beta$; compute public
$\mathbf w' = A\mathbf z - c\mathbf t_1 2^d$ and $\mathbf h$ (BCC0:
$\mathbf 0$; BCC+: $h_j=[\mathrm{HighBits}(w'_j)\neq w_{1,j}]$); reject if
$\mathrm{wt}(\mathbf h) > \omega$; emit $\textsc{sigEncode}(\tilde
c,\mathbf z,\mathbf h)$; assert unmodified FIPS 204 verify (failure $=$
bug).

\section{Fallback (Option 3)}
If unmodified-FIPS-204-byte-equality is not mandatory, use the
Raccoon/Ringtail-style threshold-friendly hint scheme --- this is exactly
the \textbf{Corona} route (\texttt{luxfi/corona}, LP-4440): public
threshold signature, leaderless, no MPC/TEE, but \emph{not} FIPS-byte-
equal.

\section{Scale / consensus notes}
For $\sim$1000+ validators: generate boundary-safe nonce certs
continuously offline; online consensus only tree-aggregates $\mathbf z$
shares; the final signature is ordinary ML-DSA; the QC carries the signer
bitmap $+$ transcript root. Do \emph{not} boundary-filter online per
message.

\section{Practical risks}
(1) usable safe-nonce rate; (2) the conditioned-nonce distribution proof;
(3) exact FIPS boundary classification (against \texttt{Decompose}, not
integer rounding); (4) keeping the margin small enough for yield while
covering $c\,\mathbf s_2$. If BCC+ yield is poor, prefer \textsc{2B nonce
shaping} (with its distribution proof) over weakening the margin.

\section{Phased plan + TALUS alignment}
\textbf{Phase 1:} BCC+ as above --- this spec, Lemmas~\ref{lem:bcc0},
\ref{lem:bccplus} machine-checked (\texttt{Crypto/Pulsar/Boundary\-
Clearance.lean}) against the FIPS \texttt{Decompose}/\texttt{HighBits}/
\texttt{MakeHint}/\texttt{UseHint} definitions, Go impl reusing the
existing \texttt{decompose}/\texttt{power2Round} primitives, the
regression / no-residual / distribution / CIRCL$+$pq-crystals interop
tests on the BCC path, and the offline-yield measurement.
\textbf{Phase 2:} \textsc{2B nonce shaping} if yield demands, with the
distribution proof. \textbf{Phase 3:} align terminology and proof
obligations with the TALUS boundary-clearance / carry-elimination
construction.
\end{document}
